Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-01-30 src/tex/ms.tex
Add to-do items
abstract

\begin{abstract}
    One of the major problems physicists face nowadays is that Einstein's theory of general relativity (GR) does not agree with quantum theories at some length scales.
    In recent decades, theorists have worked on many beyond-GR theories to unify both.
    Some of these theories, such as Chern-Simons gravity, suggest that there is gravitational wave (GW) amplitude birefringence.
    In our study, we perform parameter estimation (PE) to constrain the strength of GW amplitude birefringence.
    Compared to previous studies, we performed PE on more events, including events in the third LIGO-Virgo catalog (GWTC-3), and used a more realistic birefringence model to describe the phenomenon.
    We obtained a constraint tighter than previous studies for an order of magnitude.
\end{abstract}

>>>>

\begin{abstract}
    The propagation of gravitational waves can reveal fundamental feature of the structure of spacetime.
    For instance, differences in the propagation of gravitational-wave polarizations would be a smoking gun of parity violations in the gravitational sector, as expected from birefringent theories like Chern-Simons gravity.
    Here we look for evidence of amplitude birefringence in the latest LIGO-Virgo catalog (GWTC-3) through the use of birefringent templates inspired by dynamical Chern-Simons gravity.
    From 70 binary-black-hole signals, we obtain the most precise constraints on amplitude birefringence yet, an order of magnitude more stringent than previous results.
\end{abstract}
